Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-12-22 main.tex
small change in the beginning of experimental evaluation

    We first describe the set of workflows used for the evaluation, and then the clusters on which the
    workflows are scheduled.

>>>>

    Before presenting the results, we first describe the set of workflows we used for the evaluation, and then the clusters on which the
    workflows were scheduled.
We also explain the way the runtime system works and interacts with our scheduler.
